### 2017-11-28 Risk analysis/Text/Layout/Layout/chapter4_discussion.tex
Added convergence diagnostics and Bayes network. Almost finished!

	The position and separation of their Bayes actions, i.e.\ their decisions, manifested according to the properties of the value distributions. These were in turn determined by the proportionality regarding distribution modes, their relative probabilities and distances to each other. This was often indicated by the position of mean and median relative to these modes. A mean located in the middle between two widely separated modes, which might be of low intrinsic uncertainty themselves, would indicate a much higher overall decision uncertainty, than a mean found in the middle of a narrow unimodal distribution. Pronounced bimodality between two extremes, i.e. high uncertainty, resulted in a wider separation of Bayes estimators. Reduction of the distribution to one mode conversely led to the convergence of different Bayes actions. A decrease in decision uncertainty furthermore was accompanied by a reduction in expected loss for each Bayes estimator. 
	Considering these observations, we derive that the degree of Bayes action convergence and respective expected losses, i.e. Bayes risks, can be considered measures for the state of knowledge and decision uncertainty at the moment of making a decision. The better these are, the more similar the decisions of differently risk-affine actors and the lower their loss expectations are. It can be assumed, that given perfect information, all actors would bid on the same estimate (the true value) and expect no loss, since no risk is present. It furthermore follows from this that the relevance of risk factors decreases with higher reduction of decision uncertainty.

@@

	Cases of various states of knowledge and decision uncertainties, i.e. different realizations of the value probability distribution, were attained by the implementation of Bayesian inference. While in most settings, adding information via inference led to a reduction of decision uncertainty, this was not always the case. We observed that the impact on decision uncertainty, induced by Bayesian inference, is not necessarily strictly aligned with the change in uncertainty regarding model parameters and their combinations. In respect to this, two aspects seems to be of central importance: (1) "where" in the model uncertainty is reduced, i.e. in which spatial area or regarding which model parameters and (2) which possible outcome is enhanced in terms of probability. An increased probability of a thick or thin seal in our 3D model, for example, equally reduced decision uncertainty significantly, by raising the probability of a positive or negative outcome, respectively. Improved certainty about our reservoir thickness, however, had little to no impact on decision-making. This shows us that some areas and parameters of the model have a much greater influence on the decision uncertainty than others.\\

@@

		%This state of knowledge and the decision uncertainty accordingly experienced alterations related to the different Bayesian inference cases. These changes related foremost to modes in the value distribution. For both model designs (1D and 3D), the prior value probability distributions were characterized by a distinct bimodality formed by widely separated modes of opposing values, i.e. one in the range of highly positive values, another at zero or negative values. By introducing likelihood functions, these modes were most often shifted or altered in their shape. The latter was observed as either an amplification of the mode, by raising its mean probability, while narrowing the range of probabilities (i.e. reducing the standard deviation), or the opposite, a diminishment of the mode up to total erasure of its probability.\\

@@

		\caption{ROV distribution of the prior model subdivided by modes into scenarios which could pose decision options (marked by greens lines). Red lines indicated a discretization of decision options according fixed scales of resource allocations for a project. For both cases, zero equals the option to "take no action", i.e. to allocate no resources.}\label{fig:scenarios_options}

@@

	It has too be emphasized that the models constructed in this work were synthetic and not based on real data. Nevertheless, the 3D model in particular was designed to include some typical structural characteristics related to hydrocarbon systems. We developed algorithms aimed to consider the most common conditions that define structural traps. The fact that similar observations were made for the 1D, as well as the 3D model, indicates a certain degree of continuity with respect to representativity. However, we also need to address that the uncertainties employed in the 3D model related to $z$-axis positional values only and were thus of primarily one-dimensional nature. This may in part account for the parallelism to the 1D model results. Furthermore, it follows that no effective uncertainty concerning the overall structural shape was implemented, particularly regarding anticlinal features and the position of the spill point in relation to the trap top. Due to this, trap volumes tended to occur primarily in distinct "filled-to-spill" scenarios. While being unrealistic, this enabled the recognition of pronounced influences related to the various control mechanisms.\\	
	For the purpose of a conceptual application, the customization of the loss functions was kept relatively simple. We argue that despite its simplicity, the design of the function and the incorporation of a risk factor was suitable to achieve a clear distinction between differently risk-affine actors and respective behavior. It would be possible to extend this design to attain very complex loss functions. As the loss function in this work was designed based on only a few basic assumptions, it might be more generally representative than a complex function that takes into account numerous very specific aspects. The consideration of more details, without a basis on real data, would have furthermore required extensive speculation, which would have presumably impaired the generalization potential of respective observations. While standard loss functions only return mean or median as estimates, loss function customization offers a flexible approach to express different objective and subjective weighting factors that are specified to certain decision-making environments and decision-makers' perspectives.

>>>>

	The position and separation of their Bayes actions, i.e.\ their decisions, manifested according to the properties of the value distributions. These were in turn determined by the proportionality regarding distribution modes, their relative probabilities and distances to each other. This was often indicated by the position of mean and median relative to these modes. A mean located in the middle between two widely separated modes, which might be of low intrinsic uncertainty themselves, would indicate a much higher overall decision uncertainty, than a mean found in the middle of a narrow unimodal distribution. Pronounced bimodality between two extremes, i.e.\ high uncertainty, resulted in a wider separation of Bayes estimators. Reduction of the distribution to one mode conversely led to the convergence of different Bayes actions. A decrease in decision uncertainty furthermore was accompanied by a reduction in expected loss for each Bayes estimator. 
	Considering these observations, we derive that the degree of Bayes action convergence and respective expected losses, i.e.\ Bayes risks, can be considered measures for the state of knowledge and decision uncertainty at the moment of making a decision. The better these are, the more similar the decisions of differently risk-affine actors and the lower their loss expectations are. It can be assumed, that given perfect information, all actors would bid on the same estimate (the true value) and expect no loss, since no risk is present. It furthermore follows from this that the relevance of risk factors decreases with higher reduction of decision uncertainty.

@@

	Cases of various states of knowledge and decision uncertainties, i.e.\ different realizations of the value probability distribution, were attained by the implementation of Bayesian inference. While in most settings, adding information via inference led to a reduction of decision uncertainty, this was not always the case. We observed that the impact on decision uncertainty, induced by Bayesian inference, is not necessarily strictly aligned with the change in uncertainty regarding model parameters and their combinations. In respect to this, two aspects seems to be of central importance: (1) "where" in the model uncertainty is reduced, i.e.\ in which spatial area or regarding which model parameters and (2) which possible outcome is enhanced in terms of probability. An increased probability of a thick or thin seal in our 3D model, for example, equally reduced decision uncertainty significantly, by raising the probability of a positive or negative outcome, respectively. Improved certainty about our reservoir thickness, however, had little to no impact on decision-making. This shows us that some areas and parameters of the model have a much greater influence on the decision uncertainty than others.\\

@@

		%This state of knowledge and the decision uncertainty accordingly experienced alterations related to the different Bayesian inference cases. These changes related foremost to modes in the value distribution. For both model designs (1D and 3D), the prior value probability distributions were characterized by a distinct bimodality formed by widely separated modes of opposing values, i.e. one in the range of highly positive values, another at zero or negative values. By introducing likelihood functions, these modes were most often shifted or altered in their shape. The latter was observed as either an amplification of the mode, by raising its mean probability, while narrowing the range of probabilities (i.e.\ reducing the standard deviation), or the opposite, a diminishment of the mode up to total erasure of its probability.\\

@@

		\caption{ROV distribution of the prior model subdivided by modes into scenarios which could pose decision options (marked by greens lines). Red lines indicate a discretization of decision options according to fixed scales of resource allocations for a project. For both cases, zero equals the option to "take no action", i.e.\ to allocate no resources.}\label{fig:scenarios_options}

@@

	It has too be emphasized that the models constructed in this work were synthetic and not based on real data. Nevertheless, the 3D model in particular was designed to include some typical structural characteristics related to hydrocarbon systems. We developed algorithms aimed to consider the most common conditions that define structural traps. The fact that similar observations were made for the 1D, as well as the 3D model, indicates a certain degree of continuity with respect to representativity. However, we also need to address that the uncertainties employed in the 3D model related to $z$-axis positional values only and were thus of primarily one-dimensional nature. This may in part account for the parallelism to the 1D model results. Furthermore, it follows that no effective uncertainty concerning the overall structural shape was implemented, particularly regarding anticlinal features and the position of the spill point in relation to the trap top. Due to this, trap volumes tended to occur primarily in distinct "filled-to-spill" scenarios. While being unrealistic, this enabled the recognition of pronounced influences related to the various control mechanisms. For computational reasons, we had to keep the number of MCMC sampling steps relatively low. For improved convergence and a higher reliability of results, more iterations should be executed. Nevertheless, we believe that for the purpose of this study, sufficient convergence and meaningful posterior results were achieved.\\	
	For a conceptual application, the customization of the loss functions was kept relatively simple. We argue that despite its simplicity, the design of the function and the incorporation of a risk factor was suitable to achieve a clear distinction between differently risk-affine actors and respective behavior. It would be possible to extend this design to attain very complex loss functions. As the loss function in this work was designed based on only a few basic assumptions, it might be more generally representative than a complex function that takes into account numerous very specific aspects. The consideration of more details, without a basis on real data, would have furthermore required extensive speculation, which would have presumably impaired the generalization potential of respective observations. We defined risk affinity to be dependent on arbitrarily chosen risk factors, which led to according re-weighting. \citet{davidson2015} used risk parameters determined by the maximal loss each actor could incur. Other approaches could be based on more tangible values, for example by making risk attitude dependent on a fixed budget. While standard loss functions only return mean or median as estimates, loss function customization offers a flexible approach to express different objective and subjective weighting factors that are specified to certain decision-making environments and decision-makers' perspectives.
